Variance reduction for MCMC methods via martingale representations

### 2020-02-17 aap/Revision/vr-mcmc-revision-new.tex
update vr-mcmc-revision-new.tex

\newcommandx{\CPE}[3][1=]{{\mathsf E}_{#1}\left[\left. #2 \, \right| #3 \right]}
\usepackage[textsize=footnotesize]{todonotes} % pour voir les commentaires

@@

@@

@@

Indeed, due to the orthonormality and completeness
of the system $\left(\phi_{k}\right)$, we have

@@

f(X_{1})=\mathsf{E}\left[f(X_{1})\right]+\sum_{k\geq1}a_{1,1,k}(X_0)\phi_{k}(\xi_{1})

@@

a_{1,1,k}(x_0)=\CPE{f(X_{1})\phi_{k}\left(\xi_{1}\right)}{X_0=x_0},
provided $\mathsf{E}\left[\left|f(X_{1})\right|^{2}\right]<\infty.$

>>>>

\def\PE{\mathsf{E}}
\newcommandx{\CPE}[3][1=]{{\mathsf E}_{#1}\left[\left. #2 \, \right| #3 \right]}
\usepackage[textsize=footnotesize]{todonotes} % pour voir les commentaires

@@

\eric{I would write \tcr{$L^2(P_\xi)$} to be coherent with the previous notations} 

@@

\begin{proof}[Proof of Theorem~\ref{prop:29032018a1}]

@@

Indeed, since $\left(\phi_{k}\right)_{k \geq 0}$ is a complete orthonormal system of , we have for all $x \in \rset^d$,
\eric{it is clear, but we must say in which sense this equality should be understood}

@@

f(X^x_{1})=\PE[f(X_{1}^x)]+\sum_{k\geq1}a_{1,1,k}(x)\phi_{k}(\xi_{1})

@@

with $a_{1,1,k}(x)=\PE[f(X_{1}^x)\phi_{k}(\xi_{1})]$, 
provided $\PE[|f(X^x_{1})|^{2}]<\infty.$
